Quantifying the manageability of pollination networks in an invasion context

### 2017-03-02 paper/manuscript.Rmd
Move details about statistical analysis to the supporting information

* **Number of words:** 148 abstract; approx. 5278 main text.

* **Number of references:** 72

@@

We also wanted to test whether invasion status or other predictors had an impact on the observed values of *n~D~*. 
We therefore used a set of generalised linear models (with binomial error structure) to investigate the effect of invasion status while also including covariates related to species richness, since one might naively expect to see a negative relationship between richness and manageability [@Menge1995]. 
These covariates included the total number of species, plant richness, pollinators richness, the ratio of plant to pollinator richness, the link density (connectance), and the study site (as a two-level factor). 
Candidate models were compared using AICc and the relative importance of the explanatory variables was evaluated using the sum of Akaike weights over candidate models that accounted for 95% of the evidence [@Burnham2003; @Bates2015; @Barton2016]. 
Coefficient estimates were averaged following @Buckland1997a while confidence intervals were calculated following @Lukacs2010.

We next explored whether real networks differ in their architecture from random ones in a concerted way that affects manageability. 
Previous research indicates a direct link between a network's degree distribution and the number of nodes necessary to fully control it [@Liu2011], but the strength and applicability of this relationship have not been tested for in weighted ecological networks. 
We therefore compared the driver-node density *n~D~* of the empirical networks to networks generated by a null model that maintained each species' strength (its total sum of visits) while allowing their degrees (its number of interactions) to vary. 
Randomisations were generated using the quasiswap-count algorithm and the function `commsim` in vegan 2.3-3 [@Oksanen2016]. 
After generating the randomised networks, we then calculated the mutual dependences and interaction asymmetries of each and determined *n~D~* using our maximum-matching framework. 
Finally, we calculated the average rank (akin to a p-value) of *n~D~* for each empirical network compared to the corresponding values of each set of 999 randomisations [@Veech2012].

Beyond network structure, the dependence asymmetry plays a fundamental role in determining the direction of control in each two-species interaction and therefore has the potential to influence the network *n~D~* results above. 
We therefore performed an additional randomisation in which we kept the structure of each network constant but randomised the direction of the interaction asymmetries. 
That is, we first calculated the observed asymmetries for each community and then shuffled the direction of the link between each pair of species. 
Similar to the other null models, we calculated the average rank of the empirical *n~D~* when compared to that of the randomisations.

@@

Our second key question was related to how species differ in their ability to drive the population dynamics of the community. 
To quantify this importance, we computed all maximal cardinality matchings in each network. 
We then calculated the frequency with which each species *i* was a driver (*f~D~*) or a superior node (*f~S~*) in the set of matchings that had a matching weight greater or equal to 0.8 times the weight of the maximum matching. 
We selected this threshold as it provided a high agreement between networks quantified by visitation and pollination efficiency as well as between our weighting/directionality assumptions; however, the choice of this threshold had a negligible impact on any results (Supporting Information S7).
Details about the computational procedure to find all maximal cardinality matchings of a network can be found in Supporting Information S1 and Figure S2.

@@

We then examined whether any species-level structural properties could predict our metrics of species importance—the frequency with which a species was a driver or a superior node (*f~D~* and *f~S~*, respectively).
We used a set of generalised linear mixed-effects models (with binomial error structure) with the relative frequencies as the response variables. 
As predictors in this model, we included measures of centrality (degree and eigen-centrality), which have been found to be strong predictors of importance in a coextinction context [@Memmott2004]; a measure related to network robustness (contribution to nestedness), as nestedness has been proposed as one of the key properties that promote stability in mutualistic networks [@Saavedra2011]; a measure of strength of association (visitation strength, the sum of visits a species receives or performs) and a measure of strength of dependence (species strength, the sum of dependences of all species on the focal species), as their distribution determines the extent of interspecific effects [@Bascompte2006].
To facilitate comparison among the continuous variables, we scaled them so that they all had a mean of zero and a standard deviation of one.
In addition, we also included guild (plant or pollinator) and whether the species is invasive or not as categorical fixed effects.
Lastly, we allowed for variation between different communities by including the network identity as a random effect [@Bates2015]. 
Although the importance of plants and pollinators or invasive and non-invasive species could respond differently to our structural metrics, our data set did not contain enough variation to include the corresponding interactions terms for these latter two predictors. 
All network metrics were calculated using the R package bipartite 2.06 [@Dormann2008]. 
Candidate models and estimates were assessed using the same procedure as in the  models for *n~D~*.

@@

All of the networks had a driver-node density *n~D~* between `r round(min(dplyr::filter(n_driver, type == "weight")$n_dr_p), digits = 2)` and `r round(max(dplyr::filter(n_driver, type == "weight")$n_dr_p), digits = 2)` (mean `r round(mean(dplyr::filter(n_driver, type == "weight")$n_dr_p), digits = 2)`; Figure 3a). 
In addition, we found that, when controlling for potential species richness effects, the *n~D~* of invaded communities was smaller to those of non-invaded communities (Figure 3b; Table S5). 
Nevertheless, of the various covariates we explored, the ratio of plants to pollinators showed the strongest relationship with *n~D~* (Table S4; Figure 3c). 
Specifically as the proportion of pollinators increases and the ratio plant/pollinator approaches unity, *n~D~* decreases (all our communities had more pollinators than plants). 
Other covariates—connectance (link density) and species richness—had negative, but comparatively less important, relationships with *n~D~*.

@@

Despite its conceptual advantages, our approach still relies on knowledge of the network of interaction between species. 
Nevertheless, our results and previous basic research show that, as long as the proportion of sampled links is enough to provide indication of the actual degree distribution (and in turn the species dependences), *n~D~*, *f~S~* and *f~D~* can still provide a simple, straightforward, and theoretically informed indication of the degree to which the community is self regulated and therefore how difficult it might be to modify its state in one way or another using some of its constituent species [Supporting Information S5; @Nepusz2012].

>>>>

* **Number of words:** 148 abstract; approx. 4,974 main text.

* **Number of references:** 65

@@

We also wanted to test whether invasion status or other predictors had an impact on the observed values of *n~D~*. 
We therefore used a set of generalised linear models (with binomial error structure) to investigate the effect of invasion status while also including covariates related to species richness, since one might naively expect to see a negative relationship between richness and manageability [@Menge1995]. 
These covariates included the total number of species, plant richness, pollinators richness, the ratio of plant to pollinator richness, the link density (connectance), and the study site (as a two-level factor).

We next explored whether real networks differ in their architecture from random ones in a concerted way that affects manageability. 
Previous research indicates a direct link between a network's degree distribution and the number of nodes necessary to fully control it [@Liu2011], but the strength and applicability of this relationship have not been tested for in weighted ecological networks. 
We therefore compared the driver-node density *n~D~* of the empirical networks to networks generated by a null model that maintained each species' strength (its total sum of visits) while allowing their degrees (its number of interactions) to vary. 
Beyond network structure, the dependence asymmetry plays a fundamental role in determining the direction of control in each two-species interaction and therefore has the potential to influence the network *n~D~* results above. 
We therefore performed an additional randomisation in which we kept the structure of each network constant but randomised the direction of the interaction asymmetries. 
That is, we first calculated the observed asymmetries for each community and then shuffled the direction of the link between each pair of species.

Additional details about the statistical models and the randomisations can be found in the Supporting Information S7.

@@

Our second key question was related to how species differ in their ability to drive the population dynamics of the community. 
To quantify this importance, we computed all maximal cardinality matchings in each network. 
We then calculated the frequency with which each species *i* was a driver (*f~D~*) or a superior node (*f~S~*) in the set of matchings that had a matching weight greater or equal to 0.8 times the weight of the maximum matching. 
We selected this threshold as it provided a high agreement between networks quantified by visitation and pollination efficiency as well as between our weighting/directionality assumptions; however, the choice of this threshold had a negligible impact on any results (Supporting Information S8).
Details about the computational procedure to find all maximal cardinality matchings of a network can be found in Supporting Information S1 and Figure S2.

@@

We then examined whether any species-level structural properties could predict our metrics of species importance—the frequency with which a species was a driver or a superior node (*f~D~* and *f~S~*, respectively).
We used a set of generalised linear mixed-effects models (with binomial error structure) with the relative frequencies as the response variables. 
As predictors in this model, we included measures of centrality (degree and eigen-centrality), which have been found to be strong predictors of importance in a coextinction context [@Memmott2004]; a measure related to network robustness (contribution to nestedness), as nestedness has been proposed as one of the key properties that promote stability in mutualistic networks [@Saavedra2011]; a measure of strength of association (visitation strength, the sum of visits a species receives or performs) and a measure of strength of dependence (species strength, the sum of dependences of all species on the focal species), as their distribution determines the extent of interspecific effects [@Bascompte2006].
In addition, we also included guild (plant or pollinator) and whether the species is invasive or not as categorical fixed effects.
Lastly, we allowed for variation between different communities by including the network identity as a random effect [@Bates2015]. 
Supplementary details about the statistical models can be found in the Supporting Information S7.

@@

All of the networks had a driver-node density *n~D~* between `r round(min(dplyr::filter(n_driver, type == "weight")$n_dr_p), digits = 2)` and `r round(max(dplyr::filter(n_driver, type == "weight")$n_dr_p), digits = 2)` (mean `r round(mean(dplyr::filter(n_driver, type == "weight")$n_dr_p), digits = 2)`; Figure 3a). 
In addition, we found that, when controlling for potential species richness effects, the *n~D~* of invaded communities was smaller to those of non-invaded communities (Figure 3b). 
Nevertheless, of the various covariates we explored, the ratio of plants to pollinators showed the strongest relationship with *n~D~* (Figure 3c; Table S5). 
Specifically as the proportion of pollinators increases and the ratio plant/pollinator approaches unity, *n~D~* decreases (all our communities had more pollinators than plants). 
Other covariates—connectance (link density) and species richness—had negative, but comparatively less important, relationships with *n~D~*.

@@

### 2017-03-02 paper/supporting_information.Rmd
Move details about statistical analysis to the supporting information

@@

# Statistical models

>>>>

# Statistical methods

## Manageability

### Genrealised linear models for *n~D~*

Candidate models were compared using AICc and the relative importance of the explanatory variables was evaluated using the sum of Akaike weights over candidate models that accounted for 95% of the evidence [@Burnham2003; @Bates2015; @Barton2016]. 
Coefficient estimates were averaged following @Buckland1997a while confidence intervals were calculated following @Lukacs2010.
Only models that accounted for 95% of the evidence weight were considered to quantify the relative importance of the fixed effects.

### Network randomisations

Randomisations that maintained the degree of the visitation networks were generated using the quasiswap-count algorithm and the function `commsim` in vegan 2.3-3 [@Oksanen2016]. 
After generating the randomised networks, we then calculated the mutual dependences and interaction asymmetries of each and determined *n~D~* using our maximum-matching framework. 
Finally, we calculated the average rank (akin to a p-value) of *n~D~* for each empirical network compared to the corresponding values of each set of 999 randomisations [@Veech2012].

Similar as in the previous null model, to evaluate the effect of the direction of the asymmetries, we calculated the average rank of the empirical *n~D~* when compared to that of the randomisations.

## Relative importance

### Genrealised mixed effects models for *f~S~* and *f~D~*

To facilitate comparison among the continuous variables, we scaled them so that they all had a mean of zero and a standard deviation of one. 
Although the importance of plants and pollinators or invasive and non-invasive species could respond differently to our structural metrics, our data set did not contain enough variation to include the corresponding interactions terms for these latter two predictors. 
All network metrics were calculated using the R package bipartite 2.06 [@Dormann2008]. 
Candidate models and estimates were assessed using the same procedure as in the  models for *n~D~*.

@@

# *n~D~* models results
